Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-01 Cover_letter_JPM.tex
fixed compiler problems
Updates from Overleaf

\documentclass[preprint,12pt]{elsarticle}
% Extended revision and answer question (2 reviewers)
% for JPM-1174473
%Since April 19, 2021
%Please resubmit your revised manuscript through the following link:
% https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f
\usepackage{tikz-imagelabels} % for  tikz
\usepackage{siunitx} % for  1e-10 scientific notation
\usepackage[bf]{caption}
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}

@@

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
\newacronym{degs}{DEGs}{differentially expressed genes}

@@

\begin{MyColorPar}{red}
" %discussion: the third limitation
There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features related to holistic care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
"

%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」

@@

\end{MyColorPar} %red
\end{MyColorPar} % blue

@@

\begin{MyColorPar}{red}
% TCGA_HNSCC_marginSFP.R [line 111] cutoffReturn <- cutofFinder_func_HNSCC.R
% retrieving optimized (minimal) p value of each Kaplan-Meier plot 
% **A summary table of P-value, Z-score standardization from all HNSCC_survival*.Rda 
% 不必每次重 run (saved at HNSCC_OS_marginS_pvalueKM_candidate_cox.Rda)
% variable name: candidate_sample (with gene symbol and KM p value), candidate_cox, n_percent_Bonferroni
%=> FDR() or p.adjust() The FDR function uses the Benjamini & Hochberg (\cite{Benjamini1995a}) ("BH", alias "fdr") correction by default.
% analysis_export.R [line 197] has FDR < 0.05 for filtering (done)
% [line 196] OS_pvalueS$p_value_adj_FDR <- p.adjust(OS_pvalue$p_OS, method='fdr')

% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
"
The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} shows which genes should be retained for subsequent univariate and multivariate analysis.
% of Cox modeling
It ensures the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
"
\end{MyColorPar} % red

@@

\begin{MyColorPar}{red}

@@

(In the section of Materials and Methods)\\
%RefSeq Release 38 (November 7, 2009)  GSE65858
%[Dataset]
"
The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
R package of GEOquery\cite{Sean2007} was used to
download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
There are 270 HNSCC participants involved in this cohort.
%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009). % (RefSeq) 
GSE65858 is a dataset for candidate selection in our workflow.
We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
"

(In the section of Results)\\
"
TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

% [2021/06/13-17] GSE65858
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the significance of the other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
%This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
"
%The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
%by GEO GSE2837 HNSCC dataset (PrognoScan)
%After the discovery by our workflow, we validated the those 20 genes in the other independent \acrshort{hnscc} cohort (GSE2837).
%The survival significance (Kaplan-Meier \textit{P} value) is in the following probes among 10 genes:\\
%1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
%2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
%17 out of 20 candidates

(In the Discussions section)\\
%[more in the discussion section]
"  % (ok)
Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
The effect size is the magnitude of the difference (or relationship) among comparing groups.
%A \textit{P} value is a tool to help interpret findings from biomedical research.
%In reporting and interpreting studies, both 
%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
While statistical significance can inform the researcher whether an effect exists, 
the \textit{P} value will not directly tell the effect size.
%The effect size is the main finding of a quantitative study.
%Statistical significance depends upon both sample size and effect size. 
The effect size is independent of the sample size\cite{Sullivan2012}.

@@

\end{MyColorPar} % red

@@

\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
"
The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data. It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x., death) at time t. It can be estimated as follow:

@@

In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
All covariates have been pooled in the hazard function h(t) to estimate their impact on the overall survival.
"
\end{MyColorPar} % red

@@

\begin{MyColorPar}{red}
% inserted at \subsubsection{From TCGA to expression biomarkers}

@@

Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\

@@

%
"

%%%%%%%%%
\end{MyColorPar} % red

@@

\begin{MyColorPar}{red}
%%%
"
There are three essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.

@@

\end{MyColorPar} % end of red

@@

\section{end_document}
\end{document}

>>>>

\documentclass[preprint,12pt]{elsarticle}
% Extended revision and answer question (2 reviewers)
% for JPM-1174473
%Since April 19, 2021
%Please resubmit your revised manuscript through the following link:
% https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f

\newenvironment{MyIndent}
{\par\leftskip1cm\relax\rightskip1cm\relax}
{\par\leftskip0cm\relax\rightskip0cm\relax}

\usepackage{tikz-imagelabels} % for  tikz
\usepackage{siunitx} % for  1e-10 scientific notation
\usepackage[bf]{caption}
\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}

@@

%%% for abbreviations, or acronyms
\usepackage[acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
\newacronym{degs}{DEGs}{differentially expressed genes}

@@

\begin{MyIndent}
\begin{MyColorPar}{red}
" %discussion: the third limitation
There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features related to holistic care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
"
\end{MyColorPar} %red
\end{MyIndent}
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」

@@

@@

\begin{MyIndent}
\begin{MyColorPar}{red}
% TCGA_HNSCC_marginSFP.R [line 111] cutoffReturn <- cutofFinder_func_HNSCC.R
% retrieving optimized (minimal) p value of each Kaplan-Meier plot 
% **A summary table of P-value, Z-score standardization from all HNSCC_survival*.Rda 
% 不必每次重 run (saved at HNSCC_OS_marginS_pvalueKM_candidate_cox.Rda)
% variable name: candidate_sample (with gene symbol and KM p value), candidate_cox, n_percent_Bonferroni
%=> FDR() or p.adjust() The FDR function uses the Benjamini & Hochberg (\cite{Benjamini1995a}) ("BH", alias "fdr") correction by default.
% analysis_export.R [line 197] has FDR < 0.05 for filtering (done)
% [line 196] OS_pvalueS$p_value_adj_FDR <- p.adjust(OS_pvalue$p_OS, method='fdr')

% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
"
The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} shows which genes should be retained for subsequent univariate and multivariate analysis.
% of Cox modeling
It ensures the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
"
\end{MyColorPar} % red
\end{MyIndent}

@@

\begin{MyIndent}
\begin{MyColorPar}{red}

@@

\textcolor{blue}{In the section of Materials and Methods}\\
%RefSeq Release 38 (November 7, 2009)  GSE65858
%[Dataset]
"
The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
R package of \\GEOquery\cite{Sean2007} was used to
download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/\\geo2r/?\\acc=GSE65858). 
GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
There are 270 HNSCC participants involved in this cohort.
%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009). % (RefSeq) 
GSE65858 is a dataset for candidate selection in our workflow.
We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
"

\textcolor{blue}{In the section of Results}\\
"
TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

% [2021/06/13-17] GSE65858
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the significance of the other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
%This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
"\\[0.3cm]
%The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
%by GEO GSE2837 HNSCC dataset (PrognoScan)
%After the discovery by our workflow, we validated the those 20 genes in the other independent \acrshort{hnscc} cohort (GSE2837).
%The survival significance (Kaplan-Meier \textit{P} value) is in the following probes among 10 genes:\\
%1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
%2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
%17 out of 20 candidates

\textcolor{blue}{In the Discussions section}\\
%[more in the discussion section]
"  % (ok)
Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
The effect size is the magnitude of the difference (or relationship) among comparing groups.
%A \textit{P} value is a tool to help interpret findings from biomedical research.
%In reporting and interpreting studies, both 
%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
While statistical significance can inform the researcher whether an effect exists, 
the \textit{P} value will not directly tell the effect size.
%The effect size is the main finding of a quantitative study.
%Statistical significance depends upon both sample size and effect size. 
The effect size is independent of the sample size\cite{Sullivan2012}.

@@

\end{MyColorPar} % red
\end{MyIndent}

@@

\begin{MyIndent}
\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
"
The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data. It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x., death) at time t. It can be estimated as follow:

@@

In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
All covariates have been pooled in the hazard function h(t) to estimate their impact on the overall survival.
"
\end{MyColorPar} % red
\end{MyIndent}

@@

\begin{MyIndent}
\begin{MyColorPar}{red}
% inserted at \subsubsection{From TCGA to expression biomarkers}

@@

Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.
"

@@

%

%%%%%%%%%
\end{MyColorPar} % red
\end{MyIndent}

@@

\begin{MyIndent}
\begin{MyColorPar}{red}
%%%
"
There are three essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.

@@

\end{MyColorPar} % end of red
\end{MyIndent}

@@

%\section{end_document}
\end{document}
